Fractional Types

### 2016-12-16 typespp.tex
sec 4

The last new syntactic category in $\Pi^/$ is that of values which deserves some background discussion. When the types denote sets, it is evident what it means to have a value of a given type: it is just an element of the set. When types denote groupoids, it is less clear what it means to have a value, especially when the total number of values, as reported by the groupoid cardinality, is a proper fraction. In that case we the values up to an equivalence relation. The idea is not uncommon: in the conventional $\lambda$-calculus, we list $\lambda x.x$ and $\lambda y.y$ as separate values of type $\tau \rightarrow \tau$ and then provide a separate equivalence relation ($\alpha$-equivalence) to express the fact that these two values are indistinguishable. The treatment in our setting is similar: for iteration groupoids $\order{c}$, every distinct iterate $c^k$ is a listed as a separate value with the understanding that some iterates are $\idisotwo$-equivalent. Similarly for symmetry groupoids $\iorder{c}$, every morphism is listed as a value $1/c^k$ with the same understanding that that some of these morphisms are $\idisotwo$-equivalent.

>>>>

The last new syntactic category in $\Pi^/$ is that of values which deserves some background discussion. When the types denote sets, it is evident what it means to have a value of a given type: it is just an element of the set. When types denote groupoids, it is less clear what it means to have a value, especially when the total number of values, as reported by the groupoid cardinality, is a proper fraction. In that case we the values up to an equivalence relation. The idea is not uncommon: in the conventional $\lambda$-calculus, we list $\lambda x.x$ and $\lambda y.y$ as separate values of type $\tau \rightarrow \tau$ and then provide a separate equivalence relation ($\alpha$-equivalence) to express the fact that these two values are indistinguishable. The treatment in our setting is similar: for iteration groupoids $\order{c}$, every distinct iterate $c^k$ is a listed as a separate value with the understanding that some iterates are $\isotwo$-equivalent. Similarly for symmetry groupoids $\iorder{c}$, every morphism is listed as a value $1/c^k$ with the same understanding that that some of these morphisms are $\isotwo$-equivalent.
